---
title: "ESM 206 Lab 10"
author: "Logan Ossentjuk"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

# New Packages 
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)

```

## beebr beeps

Use function `beep()` in the beepr package to make an aurio alert when your code is done working 


```{r, eval = FALSE} 
#eval = FALSE makes it not get run when you knit 

for(i in rev(seq(1:9999))) {
  
  print(paste(i , "bottles of beer on the wall"))
}

beep(6)
```


## praise and cowsay

Packages built with a single purpose: to be kind and fun 

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

Use `cowsay::say()` to make a character say something to you 

```{r}
say("Waddup", by = "hypnotoad")
```

#To create a version controlled project from a local project

```{r, eval = FALSE}
# Run the below code in the consol 

#usethis::use_git()
- select yes
- select yes again
#usethis::use_github()
run
```


## Use `paletteer` to access thousands of color palletts

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) + 
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("beyonce::X87")

```

## One spatial data example 

```{r}
#sf packages: simple features 
# for spatial data 

vegetation <- read_sf("doc.kml") %>% 
  select(Name) %>% 
  clean_names()

ggplot(data = vegetation) +
  geom_sf(aes(fill = name), color = NA) + 
  scale_fill_paletteer_d("palettetown::magneton") +
  theme_minimal()

# Update theme to theme_minimal
# Change fill color based on vegetation type 
# Set color of the line to NA (color = NA)
```

```{r}
ggsave(filename = "my_awesome_map.jpg", width = 8, height = 5)
```

